A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-19 paper/aosgflp.tex
Modify appendix

% \section*{Acknowledgment}    
% The authors express their gratitude to Dr. \hspace{-.5em} Meeker for his comments and suggestions.

@@

\section{Definition of global average for Model 4}
\label{global-avg}
In Section \ref{model-assessment}, to illustrate the concept of shrinkage in our hierarchical model, we refer to a `global average' which represents an average GLFP cdf for the entire population, $\op{GLFP}\left(\bar{\pi},\mu_1,\sigma_1,\bar{\mu}_2,\bar{\sigma}_2\right)$. For the parameters that vary across drive models, we select values corresponding to the medians of the hierarchical distributions (Eq. \ref{eq:hier-model}) conditional on the hyperparameters. In particular, setting
$$\bar{\pi}=\op{logit}^{-1}(\eta_{\pi}),\;\bar{\mu}_2=\eta_{t_2} - m_{\sigma_2}\Phi^{-1}(.2) \mbox{ and } \bar{\sigma}_2= m_{\sigma_2}.$$
Let $F(\cdot|a,b),\;F^{-1}(\cdot|a,b)$ denote the cdf and inverse cdf, respectively, for a log-normal distribution with log-location parameter $a$ and log-scale parameter $b$. Then
$$m_{\sigma_2}=F^{-1}[0.5 \cdot F(1|\eta_{\sigma_2},\tau_{\sigma_2})|\eta_{\sigma_2}, \tau_{\sigma_2}],$$
which is the median of a log-normal distribution with parameters $\eta_{\sigma_2}$, and $\tau_{\sigma_2}$, truncated to the interval $(0, 1)$.

We estimate the global average pointwise, using draws from the joint posterior distribution, $\left(\eta_\pi^{(s)}, \mu_1^{(s)}, \sigma_1^{(s)}, \eta_{t_2}^{(s)},\eta_{\sigma_2}^{(s)},\tau_{\sigma_2}^{(s)}\right)$, $s=1,2,\ldots,S$. The computation is thus similar to that shown in Equation \ref{pointwise-medians}.
 % We get this by setting the $\op{GLFP}$ parameters equal to the median of their hierarchical distribution, i.e., $\pi=\op{logit}^{-1}(\eta_{\pi}^{(s)}),\, \mu_1=\mu_1^{(s)},\, \sigma_1=\sigma_1^{(s)},\, \mu_2=\eta_{t_2}^{(s)} - m_{\sigma_2}^{(s)} \Phi_{SEV}^{-1}(.2)$ and $\sigma_2= m_{\sigma_2}^{(s)}$, where $m_{\sigma_2}^{(s)}=F^{-1}[0.5 \cdot F(1;\eta_{\sigma_2}^{(s)},\tau_{\sigma_2}^{(s)});\eta_{\sigma_2}^{(s)}, \tau_{\sigma_2}^{(s)}]$ is the population median of the $\sigma_{2g}$, conditioning on $\left(\eta_{\sigma_2}^{(s)},\tau_{\sigma_2}^{(s)}\right)$. The curve was estimated using pointwise medians as in Equation \ref{pointwise-medians}.
\section{Online Supplementary Material}
\label{sec:supple}
\begin{supplement}[id=suppA]
  \sname{Supplement A}
  \stitle{Stan Code and Plots}
  \slink[doi]{COMPLETED BY THE TYPESETTER}
  \sdatatype{.pdf}
  \sdescription{Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6.}
\end{supplement}

>>>>

\section*{Acknowledgment}    
The authors express their gratitude to Nick Clark for his comments and suggestions.

@@

\section{Definition of global average for Model 4}
\label{global-avg}
In Section \ref{model-assessment}, to illustrate the concept of shrinkage in our hierarchical model, we refer to a `global average' which represents an average GLFP cdf for the entire population, $\op{H}\left(\cdot|\bar{\pi},\mu_1,\sigma_1,\bar{\mu}_2,\bar{\sigma}_2\right)$. Since $\mu_1$ and $\sigma_1$ are shared across drive-models, these can already be interpreted as `global'. For the parameters that vary across drive models, we select values corresponding to the medians of the hierarchical distributions (\ref{eq:hier-model}) conditional on the hyperparameters. In particular, setting
$$\bar{\pi}=\op{logit}^{-1}(\eta_{\pi}),\;\bar{\mu}_2=\eta_{t_2} - m_{\sigma_2}\Phi^{-1}(.2) \mbox{ and } \bar{\sigma}_2= m_{\sigma_2}.$$
Let $F(\cdot|a,b),\;F^{-1}(\cdot|a,b)$ denote the cdf and inverse cdf, respectively, for a log-normal distribution with log-location parameter $a$ and log-scale parameter $b$. Then
$$m_{\sigma_2}=F^{-1}[0.5 \cdot F(1|\eta_{\sigma_2},\tau_{\sigma_2})|\eta_{\sigma_2}, \tau_{\sigma_2}],$$
which is the median of a log-normal distribution with parameters $\eta_{\sigma_2}$, and $\tau_{\sigma_2}$, truncated to the interval $(0, 1)$.

We estimate the global average pointwise, using draws from the joint posterior distribution, $H\left(\tilde{t}|\eta_\pi^{(s)}, \mu_1^{(s)}, \sigma_1^{(s)}, \eta_{t_2}^{(s)},\eta_{\sigma_2}^{(s)},\tau_{\sigma_2}^{(s)}\right)$, $s=1,2,\ldots,S$. The computation is thus similar to that shown in (\ref{pointwise-medians}).
 % We get this by setting the $\op{GLFP}$ parameters equal to the median of their hierarchical distribution, i.e., $\pi=\op{logit}^{-1}(\eta_{\pi}^{(s)}),\, \mu_1=\mu_1^{(s)},\, \sigma_1=\sigma_1^{(s)},\, \mu_2=\eta_{t_2}^{(s)} - m_{\sigma_2}^{(s)} \Phi_{SEV}^{-1}(.2)$ and $\sigma_2= m_{\sigma_2}^{(s)}$, where $m_{\sigma_2}^{(s)}=F^{-1}[0.5 \cdot F(1;\eta_{\sigma_2}^{(s)},\tau_{\sigma_2}^{(s)});\eta_{\sigma_2}^{(s)}, \tau_{\sigma_2}^{(s)}]$ is the population median of the $\sigma_{2g}$, conditioning on $\left(\eta_{\sigma_2}^{(s)},\tau_{\sigma_2}^{(s)}\right)$. The curve was estimated using pointwise medians as in Equation \ref{pointwise-medians}.
\section{Online Supplementary Material}
\label{sec:supple}
\begin{supplement}[id=suppA]
  \sname{Supplement A}
  \stitle{Stan Code and Plots}
  \slink[doi]{COMPLETED BY THE TYPESETTER}
  \sdatatype{.pdf}
  \sdescription{Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6.}
\end{supplement}
